---
title: "Use MNI NIFIT to create subcortical ROI mask in CIFTI"
author: "Joern Alexander Quent"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Aim
Here, I will try to use a MNI NIFTI file to create a subcortical ROI mask in CIFTI format. 

Thanks to @damondpham on GitHub for the code pointing to the right direction ([here](https://github.com/mandymejia/ciftiTools/issues/61)).

# Libraries used
```{r libraries}
library(oro.nifti)
library(ciftiTools)
ciftiTools.setOption("wb_path", "C:/Program Files/workbench/bin_windows64")
```

<details>
 <summary>Click here for detailed session information. </summary>

```{r session_info}
sessioninfo::session_info()
```
</details>


# Load a cifti file to use as a template
I load a z-map from a group-level analysis as a template so that the new xifti/cifti matches our data. 

```{r load_cifti_template}
# Load z-map
cifti_temp <- "E:/Seafile/imaging_results/SpaNov/OLMe_7T_SpaNov_gradient_6lvl_smo4_MSMAll/cope7.feat/stats/vwc/results_lvl2cope1_dat_ztstat_c1.dscalar.nii"
temp_xii   <- read_cifti(cifti_temp, brainstructures = "all")

# Create empty xifti based on this template
new_xii <- newdata_xifti(temp_xii, 0)
```

# Load the MNI NIFTI file
Next, I load the MNI image that I want to use as a mask for my analysis. 

```{r load_nifti}
# https://www.r-bloggers.com/2014/10/working-with-nifti-images-in-r/
ROI_nii <- readNIfTI("E:/Seafile/imaging_results/Midbrain_Atlases_all/mean_fullMB.nii.gz")
ROI_nii <- cal_img(ROI_nii) # Not sure if this is necessary
```

Based on the information below, the .nii image should be in the right format. 

```{r print_nii}
print(ROI_nii)
```

For instance, the subcortical mask of our cifti file has the following dimensions: 

```{r cifti_dim}
dim(temp_xii$meta$subcort$mask)
```


# Using nifti matrix to create a mask
As the first step, we will binary the group-level mask by rounding. 

```{r round_nii}
ROI_nii_bin <- round(ROI_nii)
```

Use the cifti mask to create a one-dimensional matrix that has the correct number of rows that we need for our cifti data (31870 data voxels). 

```{r nii_to_matrix}
# Use the subcortical mask of the cifti file to create a one-dimensional matrix/vector
subcort_mask   <- new_xii$meta$subcort$mask
subcort_matrix <- ROI_nii_bin[subcort_mask]

# Add this as new data to the xifti object
new_xii$data$subcort <- matrix(subcort_matrix, nrow = length(subcort_matrix), ncol = 1)
```

Now, `subcort_matrix` has `r length(subcort_matrix)` values, which is exactly the number of voxels in the subcortical mask of the cifti file. If everything is correct, our new object should pass the xifti test.

```{r test_xifti}
is.xifti(new_xii)
```

# Visualise the result
```{r visualise_result}
view_cifti_volume(new_xii)
```

Our ROI is supposed to cover the midbrain, which seems to be the case based on the image above. 

# Create midbrain cifti ROI file
```{r save_cifti}
write_xifti(new_xii, "E:/Seafile/imaging_results/Midbrain_Atlases_all/SN_VTA_ROI.dscalar.nii")
```
